Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-28 Articles/Article 1/main.tex
minor
interpolation, comments

@@

\add{
	- optimization algorithm \\
	- robot kinematics (include the exact-reduced method) \\
	- primary task of distance goal \\
	- secondary task of repulsive field \\
	- damped least squares \\
	- secondary task of manipulation measure \\	
	- different tasks merging equation \\
}

@@

@@

\add{	
	- object detection is done in task domain and not c-space (more logical) \\
	- repulsive field calculation - matrix "convolution" method \\
	- matrix size and shape selection \\
	- equation for repulsive kernel values (non-linear) \\
	- PLOT: (ERK) kernel graphics \\
	- PLOT: (ERK) linear kernel graphics \\
	- PLOT: kernel field shape 	\\
	- interpolation of the repulsive field \\
	- what if there are obstacles behind wall (usually not the case, depth sensors show only thin walls, some noise doesnt matter, non-linear kernel, possible additional pre-convolution to convert obstacle grid to edges) \\
	- effecient calculation in dinamic environments, lacking prediction capabilities (MPC) \\
	- good for working in "statistical, noisy" obstacle grids
}

@@

>>>>

\comment{}{optimization algorithm diagram}

@@

\add{
	- robot kinematics the exact-reduced method \\
	- secondary task of manipulation measure \\	
	- different tasks merging equation \\
}

\subsubsection{Exact Reduced Inverse Kinematics Method}

\add{
	- cite žlajpah article \\
	- explain how it works \\
	- equation \\
	- scalar simplification	
}

@@

\alert{Is this equation correct, maybe add a singularity damping factor.}

@@

\add{	
	- object detection is done in task domain and not c-space (more logical) \\
	- repulsive field calculation - matrix "convolution" method \\
	- matrix size and shape selection \\
	- equation for repulsive kernel values (non-linear) \\
	- PLOT: (ERK) kernel graphics \\
	- PLOT: (ERK) linear kernel graphics \\
	- PLOT: kernel field shape 	\\
	- what if there are obstacles behind wall (usually not the case, depth sensors show only thin walls, some noise doesnt matter, non-linear kernel, possible additional pre-convolution to convert obstacle grid to edges) \\
	- effecient calculation in dinamic environments, lacking prediction capabilities (MPC) \\
	- good for working in "statistical, noisy" obstacle grids
}

@@

Želimo, da je gibanje robota zvezno in ne skokovito. Da lahko to dosežemo je potrebno, da vsi hitrostni prispevki, ki vplivajo na robota prehajajo med seboj zvezno. Ker imamo mrežo ovir diskretno definirano, to ni res. Z zvišanjem resolucije polja ovir in se lahko zveznosti teoretično neskončno približamo, vendar pa imamo v realnosti običajno opravka z končno resolucijo. Da je velikost hitrosti kljub temu zvezna, ko prehajamo z točko interesa POI iz ene celice mreže ovir v drugo, uporabimo trilinearno interpolacijo, s katero za vsako od hitrosti v treh kartezičnih smeri posebaj interpoliramo hitrosti in dobimo zvezno in neskokovito linearno aproksimacijo pri prehodu med celicami.

\add{kako pridobimo vrednosti v okoliških celicah}
\add{zakaj vrednosti definiramo v centrih voxlov (celicah)}
\add{enačbe trilinearne interpolacije}

\add{	- interpolation of the repulsive field \\}
